---
title: "R notebook for \"Do verbs have an inherent association to specific nouns than others? A preliminary experimental study\""
author:
  - name:
      given: I Gede Semara Dharma
      family: Putra
    orcid: 0009-0000-6711-0878
    corresponding: true
    url: https://figshare.com/authors/I_Gede_Semara_Dharma_Putra/11755628
    affiliations: Universitas Udayana
    roles:
      - conceptualization: lead
      - investigation: lead
      - analysis: lead
      - methodology: lead
      - writing: lead
  - name:
      given: Gede Primahadi Wijaya
      family: Rajeg
    orcid: 0000-0002-2047-8621
    url: https://www.ling-phil.ox.ac.uk/people/gede-rajeg
    corresponding: false
    affiliations:
      - number: 1
        name: University of Oxford
      - number: 2
        name: Universitas Udayana
date: 2023-07-09
date-modified: now
google-scholar: true
appendix-cite-as: display
format: 
  html: 
    number-sections: true
---

## Pre-processing {#sec-preprocess}

Preparing the main data from the raw data output of the Gorilla experiment.

```{r}
#| label: setup
#| echo: true
#| eval: false

library(tidyverse)
library(readxl)

df_raw <- map2(.x = "data/data-raw.xlsx", 
               .y = 1:17, 
               ~read_xlsx(path = .x, sheet = .y)) |>
  map_df(bind_rows)

resp_count <- df_raw |> 
  filter(`Response Type` == "response") |> 
  select(`Participant Private ID`, Response, `Spreadsheet: Text`) |> 
  distinct() |> 
  count(`Participant Private ID`, Response, `Spreadsheet: Text`) |> 
  separate(`Spreadsheet: Text`, 
           into = c("eng_v", "idn_v"), 
           sep = "\\s\\=\\s", 
           remove = FALSE) |>
  mutate(response_ID = str_replace_all(Response, 
                                       "(^[^0-9]+(?=\\d)|\\.jpe?g$)", 
                                       "")) |> 
  filter(Response != "0")

verb_group <- data.frame(idn_v = c("Memberi", "Membuat", "Mencari", 
                                   "Mendapatkan", "Mengambil"), 
                         groups = c("E", "B", "C", 
                                    "D", "A"))

resp_count <- left_join(resp_count, 
                        verb_group, 
                        by = join_by(idn_v)) |> 
  mutate(response_ID = paste(groups, response_ID, sep = "")) |> 
  rename(participant_ID = `Participant Private ID`,
         text_stimuli = `Spreadsheet: Text`,
         response = Response)
resp_count |> 
  write_csv("data/data-main.csv")
```

## Main data {#sec-maindata}

Loading the count data for each participant.

```{r}
#| label: load-main-data
#| message: false
#| warning: false
#| error: false

library(tidyverse)
resp_count <- read_csv("data/data-main.csv")
nouns <- read_csv2("data/noun-codes.csv") |> 
  rename(response_ID = CODES)
```

Getting the summarised responses across all participants.

```{r}
#| label: summarised-responses

resp_count2 <- resp_count |> 
  group_by(eng_v, groups, response_ID) |> 
  summarise(n = sum(n), .groups = "drop") |> 
  arrange(groups) |> 
  rename(freq = n) |> 
  left_join(nouns, by = join_by(response_ID))
resp_count2
```

## Visualisation of the results {#sec-visualisation}

### TAKE group {#sec-take}

@fig-A-verb-group shows the frequency of nouns with the TAKE verb group.

```{r}
#| label: fig-A-verb-group
#| fig-cap: "Distribution of nouns for the \"TAKE\" verb groups"
#| fig-cap-location: bottom
df <- resp_count2 |> 
  filter(groups == "A") |> 
  mutate(eng_v = fct_relevel(eng_v, c("Take", "Bring", "Collect", "Gather", "Seize", "Fetch", "Hoard")),
         NOUN = fct_relevel(NOUN, c("log", "wheelbarrow", "hammer", "box"))) 
cols <- df$COLS
names(cols) <- df$NOUN

df |> 
  ggplot(aes(x = eng_v, 
             y = freq, 
             fill = NOUN)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = cols) +
  theme_bw() +
  theme(legend.position = "top") + 
  labs(y = "Frequency",
       x = "TAKE verb group",
       fill = "")
```

### MAKE group {#sec-make}

@fig-B-verb-group shows the frequency of nouns with the MAKE verb group.

```{r}
#| label: fig-B-verb-group
#| fig-cap: "Distribution of nouns for the \"MAKE\" verb groups"
#| fig-cap-location: bottom
df <- resp_count2 |> 
  filter(groups == "B") |> 
  mutate(eng_v = fct_relevel(eng_v, c("Make", "Create", "Produce", "Design", "Establish", "Construct", "Manufacture")),
         NOUN = fct_relevel(NOUN, c("carpet", "ornament", "gold bar", "paper airplane"))) 
cols <- df$COLS
names(cols) <- df$NOUN

df |> 
  ggplot(aes(x = eng_v, 
             y = freq, 
             fill = NOUN)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = cols) +
  theme_bw() +
  theme(legend.position = "top") + 
  labs(y = "Frequency",
       x = "MAKE verb group",
       fill = "")
```

### FIND group

@fig-C-verb-group shows the frequency of nouns with the FIND verb group.

```{r}
#| label: fig-C-verb-group
#| fig-cap: "Distribution of nouns for the \"FIND\" verb groups"
#| fig-cap-location: bottom

df <- resp_count2 |> 
  filter(groups == "C") |> 
  mutate(eng_v = fct_relevel(eng_v, c("Find", "Discover", "Search", "Explore", "Investigate", "Locate", "Rummage")),
         NOUN = fct_relevel(NOUN, c("milk", "items", "puzzle piece", "gold ore"))) 
cols <- df$COLS
names(cols) <- df$NOUN

df |> 
  filter(groups == "C") |> 
  ggplot(aes(x = eng_v, 
             y = freq, 
             fill = NOUN)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = cols) +
  theme_bw() +
  theme(legend.position = "top") + 
  labs(y = "Frequency",
       x = "FIND verb group",
       fill = "")
```

### GET group {#sec-get}

@fig-D-verb-group shows the frequency of nouns with the GET verb group.

```{r}
#| label: fig-D-verb-group
#| fig-cap: "Distribution of nouns for the \"GET\" verb groups"
#| fig-cap-location: bottom

df <- resp_count2 |> 
  filter(groups == "D") |> 
  mutate(eng_v = fct_relevel(eng_v, c("Get", "Receive", "Earn", "Gain", "Obtain", "Acquire", "Procure")),
         NOUN = fct_relevel(NOUN, c("money", "medal", "trophy", "television"))) 
cols <- df$COLS
names(cols) <- df$NOUN

df |> 
  ggplot(aes(x = eng_v, 
             y = freq, 
             fill = NOUN)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = cols) +
  theme_bw() +
  theme(legend.position = "top") +
  labs(y = "Frequency",
       x = "GET verb group",
       fill = "")
```

### GIVE group {#sec-give}

@fig-E-verb-group shows the frequency of nouns with the GIVE verb group.

```{r}
#| label: fig-E-verb-group
#| fig-cap: "Distribution of nouns for the \"GIVE\" verb groups"
#| fig-cap-location: bottom

df <- resp_count2 |> 
  filter(groups == "E") |> 
  mutate(eng_v = fct_relevel(eng_v, c("Give", "Provide", "Share", "Present", "Grant", "Donate", "Bestow")),
         NOUN = fct_relevel(NOUN, c("food", "t-shirt", "gift", "cup"))) 
cols <- df$COLS
names(cols) <- df$NOUN

df |>  
  filter(groups == "E") |> 
  ggplot(aes(x = eng_v, 
             y = freq, 
             fill = NOUN)) + 
  geom_col(position = "dodge") + 
  scale_fill_manual(values = cols) +
  theme_bw() +
  theme(legend.position = "top") +
  labs(y = "Frequency",
       x = "GIVE verb group",
       fill = "")
```
